Structural Divergence Analysis

### 2017-04-04 analysis-dynamical-MSF.Rmd
dinámica 4/4/17

```{r prepare_site_data}
# prepare the data
square.dif.MSF.exp = read.csv(square.dif.MSF.exp.fname, header = T)

square.dif.MSF.mut = read.csv(square.dif.MSF.mut.fname, header = T)

square.dif.MSF.medium = read.csv(square.dif.MSF.medium.fname, header = T)
```

@@

plot(mean.square.dif.MSF.exp, ylab = "Square dif MSF", xlab = "site", col = "blue")
points(mean.square.dif.MSF.mut, col = "green")
points(mean.square.dif.MSF.medium, col = "red")

>>>>

```{r prepare_site_data}
# prepare the data
square.dif.MSF.exp = read.csv(square.dif.MSF.exp.fname, header = T)
square.dif.MSF.mut = read.csv(square.dif.MSF.mut.fname, header = T)
square.dif.MSF.medium = read.csv(square.dif.MSF.medium.fname, header = T)
```

@@

plot(mean.square.dif.MSF.exp, ylab = "<Square dif MSF>", xlab = "site", col = "blue")
points(mean.square.dif.MSF.mut, col = "green")
points(mean.square.dif.MSF.medium, col = "red")

### 2017-04-04 analysis-dynamical-nH.Rmd
dinámica 4/4/17

```{r set_file_names}
# set input filenames
## data
reference.fname = file.path(data.dir, paste(family, "_ref.txt", sep = ""))
protein_list.fname = file.path(data.dir, paste(family, "_list.txt", sep = ""))
site.info.fname = file.path(data.dir, paste(p.ref, "_m.da.ca.csv", sep = ""))
min.da.CM.CA.fname = file.path(data.dir, paste(p.ref, "_min.da.CM.ca.csv", sep = ""))

@@

```{r prepare_site_data}
# prepare the data
nH.exp = read.csv(nH.exp.fname, header = T)

nH.mut = read.csv(nH.mut.fname, header = T)

nH.medium = read.csv(nH.medium.fname, header = T)
```

@@

```{r comparisson-of-means}
# calculate means
mean.nH.exp = colMeans(nH.exp, na.rm = T)
mean.nH.mut = colMeans(nH.mut)
mean.nH.medium = colMeans(nH.medium)

# scale profiles
mean.nH.exp = rank(mean.nH.exp)
mean.nH.mut = rank(mean.nH.mut)
mean.nH.medium = rank(mean.nH.medium)

plot(mean.nH.exp, ylab = "nH", xlab = "site", col = "blue")
points(mean.nH.mut, col = "green")
points(mean.nH.medium, col = "red")

>>>>

```{r set_file_names}
# set input filenames
## data
reference.fname = file.path(data.dir, paste(family, "_ref.txt", sep = ""))
protein_list.fname = file.path(data.dir, paste(family, "_list.txt", sep = ""))

@@

```{r prepare_mode_data}
# prepare the data
nH.exp = read.csv(nH.exp.fname, header = T)
nH.mut = read.csv(nH.mut.fname, header = T)
nH.medium = read.csv(nH.medium.fname, header = T)
```

@@

```{r comparisson-of-means, fig.cap = "blue = experimental - green = mut - red = medium selection"}
# calculate means
mean.nH.exp = colMeans(nH.exp, na.rm = T)
mean.nH.mut = colMeans(nH.mut)
mean.nH.medium = colMeans(nH.medium)

# scale profiles
mean.nH.exp = scale(mean.nH.exp[which(!is.na(mean.nH.exp))])
mean.nH.mut = scale(mean.nH.mut[which(!is.na(mean.nH.mut))])
mean.nH.medium = scale(mean.nH.medium[which(!is.na(mean.nH.medium))])

plot(mean.nH.exp, ylab = "<nH>", xlab = "mode", col = "blue")
points(mean.nH.mut, col = "green")
points(mean.nH.medium, col = "red")

cor.df = data.frame("comparison" = c("exp vs mut", "exp vs medium", "mut vs medium"),
                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
knitr::kable(cor.df, digits = 2)
```

```{r vs-mean-profiles}

```{r comparisson-of-means-100-modes}

# get first 100 modes and re-scale
mean.nH.exp = scale(mean.nH.exp[1:100])
mean.nH.mut = scale(mean.nH.mut[1:100])
mean.nH.medium = scale(mean.nH.medium[1:100])

plot(mean.nH.exp, ylab = "<nH>", xlab = "mode", col = "blue")
points(mean.nH.mut, col = "green")
points(mean.nH.medium, col = "red")

### 2017-04-04 analysis-dynamical-nR.Rmd
dinámica 4/4/17

```{r prepare_site_data}
# prepare the data
nR.exp = read.csv(nR.exp.fname, header = T)

nR.mut = read.csv(nR.mut.fname, header = T)

nR.medium = read.csv(nR.medium.fname, header = T)
```

@@

```{r comparisson-of-means}
# calculate means
mean.nR.exp = colMeans(nR.exp, na.rm = T)
mean.nR.mut = colMeans(nR.mut)
mean.nR.medium = colMeans(nR.medium)

# scale profiles
mean.nR.exp = rank(mean.nR.exp)
mean.nR.mut = rank(mean.nR.mut)
mean.nR.medium = rank(mean.nR.medium)

plot(mean.nR.exp, ylab = "nR", xlab = "site", col = "blue")
points(mean.nR.mut, col = "green")
points(mean.nR.medium, col = "red")

>>>>

```{r prepare_mode_data}
# prepare the data
nR.exp = read.csv(nR.exp.fname, header = T)
nR.mut = read.csv(nR.mut.fname, header = T)
nR.medium = read.csv(nR.medium.fname, header = T)
```

@@

```{r comparisson-of-means, fig.cap = "blue = experimental - green = mut - red = medium selection"}
# calculate means
mean.nR.exp = colMeans(nR.exp, na.rm = T)
mean.nR.mut = colMeans(nR.mut)
mean.nR.medium = colMeans(nR.medium)

# scale profiles
mean.nR.exp = scale(mean.nR.exp[which(!is.na(mean.nR.exp))])
mean.nR.mut = scale(mean.nR.mut[which(!is.na(mean.nR.mut))])
mean.nR.medium = scale(mean.nR.medium[which(!is.na(mean.nR.medium))])

plot(mean.nR.exp, ylab = "<nR>", xlab = "mode", col = "blue")
points(mean.nR.mut, col = "green")
points(mean.nR.medium, col = "red")

cor.df = data.frame("comparison" = c("exp vs mut", "exp vs medium", "mut vs medium"),
                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
knitr::kable(cor.df, digits = 2)
```

```{r vs-mean-profiles}

```{r comparisson-of-means-100-modes}

# get first 100 modes and re-scale
mean.nR.exp = scale(mean.nR.exp[1:100])
mean.nR.mut = scale(mean.nR.mut[1:100])
mean.nR.medium = scale(mean.nR.medium[1:100])

plot(mean.nR.exp, ylab = "<nR>", xlab = "mode", col = "blue")
points(mean.nR.mut, col = "green")
points(mean.nR.medium, col = "red")

### 2017-04-04 analysis-structure.Rmd
dinámica 4/4/17

```
```{r structure-profiles-CN-comparison}

# compare profiles
## plot
par(pty = "s")
plot(x = d.exp$mean.z.RSD, y = CN, xlab = "experimental <zRSDi>")
plot(x = d.mut$mean.z.RSD, y = CN, xlab = "theoretical with no selection <zRSDi>")
plot(x = d.strong$mean.z.RSD, y = CN, xlab = "theoretical with strong selection <zRSDi>")

>>>>

```
### sequence - structure comparison

```{r structure-profiles-CN-comparison}

# compare profiles
## plot
par(pty = "s")

plot(x = d.exp$mean.z.RSD, y = CN, xlab = "experimental <zRSDi>")
plot(x = d.mut$mean.z.RSD, y = CN, xlab = "theoretical with no selection <zRSDi>")
plot(x = d.strong$mean.z.RSD, y = CN, xlab = "theoretical with strong selection <zRSDi>")
